### 2013-02-14 doc/xps2013/proposal.tex
final pass on intro complete

\item \textbf{Reinvent network communication:} Our preliminary work has
revealed limitations of the current Grappa runtime system with regards to
network scaling. This proposal plans to enhance the network layer with whole
new forms of communication scheduling and aggregation, and explore new forms
of hardware/software interactions of remote direct memory access (RDMA).

\item \textbf{Language and compiler support:} Presently, Grappa is implemented
strictly as a library. Programmers must express remote operations explicitly
as function calls. This adds burden high-level language programmers do not
usually face and obfuscates opportunities for compiler optimizations. A
significant research thrust of the proposed work is to use language and
compilation support to provide a cleaner programming model and use
statically-available knowledge to lessen the runtime overhead automatically.

@@

Irregular computations are of increasing economic importance.  Moreover, they are key to several national security applications.  If commodity hardware can be cajoled into executing such applications efficiently it will open the door for new and rich applications.  Furthermore, irregular applications will then reap the benefits of advances in commodity processors and networks, rather than requiring custom hardware that advances only at much higher cost.  Graph queries, machine-learning and data-driven science will significantly benefit from the technology we aim to create from the ideas in this grant proposal.  In addition our work will include the construction of a comprehensive irregular benchmark suite, something to help guide our own and the field's research.

>>>>

\item \textbf{Accelerated network communication:} Our preliminary work has
revealed limitations of the current Grappa runtime system with regards to
network scaling. This proposal plans to enhance the network layer with whole
new forms of communication scheduling and aggregation, and explore new forms
of hardware/software interactions of remote direct memory access (RDMA).

\item \textbf{Language and compiler support:} Presently, Grappa is implemented
strictly as a library. Programmers must express remote operations explicitly
as function calls. This adds a burden high-level language programmers do not
usually face and obfuscates opportunities for compiler optimizations. A
significant research thrust of the proposed work is to use language and
compilation support to provide a cleaner programming model and use
statically-available knowledge to lessen the runtime overhead.

@@

Irregular computations are of increasing economic importance.  Moreover, they are key to several national security applications.  If commodity hardware can be cajoled into executing such applications efficiently it will open the door for new and rich applications.  Furthermore, irregular applications will then reap the benefits of advances in commodity processors and networks, rather than requiring custom hardware that advances only at much higher cost.  Graph queries, machine-learning and data-driven science will significantly benefit from the technology we aim to create from the ideas in this grant proposal.  In addition our work will include the construction of a comprehensive irregular benchmark suite to help guide our own and the field's research.
